---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BioinfoRtools

<!-- badges: start -->
<!-- badges: end -->

The BioinfoRtools is  A comprehensive bioinformatics R package toolbox

## Installation

You can install the development version of BioinfoRtools like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
devtools::install_github("YulongQin/BioinfoRtools")
```

## Example

This is a basic example which shows you how to conduct differential analysis of expression profiles:

```{r DEGs_DESeq2,echo=T}
library(BioinfoRtools)
ls(package:BioinfoRtools)

## basic example code
res <- DEGs_DESeq2(
  countdata=countdata,
  group=coldata$condition,
  case = "treated",
  ctrl = "untreated",
  covariate = NULL,
  updown_thres = 1,
  rate_sap = 0.1,
  OUT_df_index = FALSE,
  updown_index = FALSE,
  p_value = 0.05,
  padj_value = 0.05,
  grp_nm = "DEGs_DESeq2",
  dir_nm = "DEGs_DESeq2"
)
```

This is a basic example which shows you how to  conduct enrichment analysis of gene sets:
```{r GO_KEGG,echo=T}
GO_KEGG(
  updown = genes,
  simplify_index = F,
  maxGSSize = 500,
  grp_nm = "GO_KEGG",
  dir_nm = "GO_KEGG"
)

```

Here's how to use some of the graphing functions`PCA` and `HTmap`:

```{r PCA}
PCA(countdata=countdata,
    group=coldata$condition, 
    grp_nm = "PCA", 
    scale = T)
```

